Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-15 talk/dls2012/paper.tex
cleanup
correct some details

\item {\bf conv3x3}$\left(n\right)$: two-dimensional convolution with kernel of fixed

@@

$n\times n$ output matrix ${\bf B} = \left(b_{i,j}\right)$ and calculates each element from the input matrix

@@

for $1 \leq i \leq n$ and $1 \leq j \leq n$.
The memory for storing the matrices are again allocated outside the benchmark and $n=1000$ was used.

@@

\begin{itemize}
\item {\bf SOR}$\left(n, c\right)$: Jacobi successive over-relaxation on a $n\times n$ grid repreated $c$ times.
The same custom two-dimensional array class as described above is used to represent
the gird.
\item {\bf SparseMatMult}$\left(n, z, c\right)$: Matrix multiplication between a $n\times n$ sparse matrix,
stored in compressed-row format, and a full storage vector, stored in a normal array. The matrix has $z$ non-zero elements and the calculation is repeated $c$ times.
\item {\bf MonteCarlo}$\left(n\right)$: Monte Carlo integration by generating $n$ points uniformly distributed over the unit square and computing the ratio of those within the unit circle.
\item {\bf LU}$\left(n, c\right)$: Computes the LU factorization of a $n \times n$ matrix. The rows of the matrix is shuffled which makes the previously used two-dimensional array class unsuitable. Instead a list of arrays is used to represent the matrix. The calculation is repeated $c$ times.
\item {\bf FFT}$\left(n, c\right)$: Fast Fourier Transform of a vector with $n$ elements, represented as an array, repeated $c$ times.
\end{itemize}

>>>>

\item {\bf conv3x3}$\left(n,m\right)$: two-dimensional convolution with kernel of fixed

@@

$m\times n$ output matrix ${\bf B} = \left(b_{i,j}\right)$ and calculates each element from the input matrix

@@

for $1 \leq i \leq m$ and $1 \leq j \leq n$.
The memory for storing the matrices are again allocated outside the benchmark and $(n,m)=(1000,1000)$ 
as well as $(n,m)=(1000000,3)$ was used.

@@

\begin{itemize}
\item {\bf SOR}$\left(n, c\right)$: Jacobi successive over-relaxation on a $n\times n$ grid repreated $c$ times.
The same custom two-dimensional array class as described above is used to represent
the gird.
\item {\bf SparseMatMult}$\left(n, z, c\right)$: Matrix multiplication between a $n\times n$ sparse matrix,
stored in compressed-row format, and a full storage vector, stored in a normal array. The matrix has $z$ non-zero elements and the calculation is repeated $c$ times.
\item {\bf MonteCarlo}$\left(n\right)$: Monte Carlo integration by generating $n$ points uniformly distributed over the unit square and computing the ratio of those within the unit circle.
\item {\bf LU}$\left(n, c\right)$: LU factorization of an $n \times n$ matrix. The rows of the matrix is shuffled which makes the previously used two-dimensional array class unsuitable. Instead a list of arrays is used to represent the matrix. The calculation is repeated $c$ times.
\item {\bf FFT}$\left(n, c\right)$: Fast Fourier Transform of a vector with $n$ elements, represented as an array, repeated $c$ times.
\end{itemize}
